A geometric approach to linear and quadratic Chabauty

### 2020-06-10 MS.tex
Replaced citep by cite everywhere, and fixed some typos

\newcommand{\den}{\mathop{\mathgroup\symoperators den}\nolimits}
\newcommand{\ggd}{\mathop{\mathgroup\symoperators ggd}\nolimits}
\newcommand{\des}{\text{d.e.s.d.a.\ }}
%\newcommand{\opg}{\text{d.e.s.d.a.\ }}
\newcommand{\blokje}{\hfill $\Box$\\}
%Om je bewijs of je antwoord af te sluiten.
\newcommand{\header}[1]{\vspace{0.5cm}\framebox[\linewidth]{\textsc{Exercise #1}}\\}
\newcommand{\deel}[1]{\textbf{#1)}\ }
\newcommand{\macht}[1]{\mathcal{P}(#1)}
\newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\A}{\mathbb{A}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\G}{\mathbb{G}}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Lcal}{\mathcal{L}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\NP}{\mathcal{NP}}
\newcommand{\NPC}{\mathcal{NPC}}
\newcommand{\F}{\mathbb{F}}
\renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand{\rad}{\text{rad}}
\newcommand{\x}{x}
\newcommand{\m}{\mathfrak{m}}
\newcommand{\tensor}{\otimes}
\newcommand{\Ring}{\textbf{Rings}}
\newcommand{\Sets}{\textbf{Sets}}

@@

This was later made into an effective argument by Coleman in 1985. This was done by finding explicitly, as a power series, a differential form $\omega$ on $J_{\Z_p}$ whose Coleman integral vanishes on $J(\Z)$. Pulling $\omega$ back to $C_{\Z_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Z)$ reducing to $P$ based only on finite-precision calculations of $\omega$. Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the introductory article \citep{poonen12}.

This Coleman-Chabauty method has been greatly generalised by Kim to so called non-abelian Chabauty. He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group. Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk in 2017 famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \citep{cursedcurve}. They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.

Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty'' \citep{edixhoven20}. Their goal in this article is to make a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian. They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve inside $T(\Z_p)$ along this map.

@@

Next, in Section~\ref{section:explicit} we focus on how to perform the calculations happening in the Jacobian. Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space. We partially follow the article \citep{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.

@@

\begin{rem}
\label{rem:smoothpointsfunc}
Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p)$, $y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\widetilde{Y}_y^p \to \widetilde{X}_x^p$. This is a direct consequence of II.7.15 of \citep{hartshorne}.
\end{rem}

@@

We will prove this using results about formal group as defined in \citep{honda70}. To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
First we introduce some notation that will be used in this section. Let $R$ be a commutative ring, and $x = (x_1,\dots,x_n)$ and sometimes $y,z$ are vectors of variables. Then $R[[x]]$ denotes as usual the ring of formal powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$. With $x = (x_1,\dots,x_n)$ and $y = (y_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$. Then for $g \in R[[y]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get \[g\circ f := (g_1(f(x)),\dots,g_k(f(x)))\in R[[x]]]^k.\] This definition makes sense because $f^i$ converges to $0$, so the infinite sum $g_j(f(x))$ converges.

@@

Now we will look at the theory of formal groups, and how that will help us. For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \citep{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \diff x_j$. If the formal group is furthermore commutative, then by Proposition~1.3 of \citep{honda70} these are closed, i.e. $d\omega_j = 0$. A $1$-form $d\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$. From now on, assume $R$ has no torsion; then $R$ imbeds into $\Q \tensor R$ and, we can formally integrate $\omega$, i.e. write it as $df$ where $f \in (\Q\tensor R)[[x]]$. We make this unique by demanding that $f(0) = 0$. Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[x]]$.

In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[x]]$ such that $d\log_i = \omega_i$. Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \citep{honda70}, this logarithm satisfies $\log(x) = x \bmod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$. By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]]$, and also satisfying $\exp(x) = x \bmod (x)^2$.
\addtocounter{thm}{-1}
\begin{exmp}[continued]
Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \citep{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$. The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$ (note this is a translate of the $\log$ from analysis), and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis). Then analysis will also explicitly tell us what $\exp$ looks like: namely, $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
\end{exmp}
\addtocounter{thm}{2}

@@

Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z)_P$. There are several, sometimes ad hoc, ways of proving finiteness. We start by looking simply at calculations modulo $p$. We let $I$ denote the ideal inside $\Z_p\angle{x_1,\dots,x_r}$ generated by $\lambda_1,\dots,\lambda_{g-1}$, and $A$ the quotient $\Z_p\angle{x_1,\dots,x_r}/I$. Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from \citep{edixhoven20}.

@@

Of note is that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \citep{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction. To summarise: in proposition~\ref{prop:linchabauty} we sacrifice certainty for being to able to prove much sharper bounds. However, a simple heuristic analysis shows that the conditions are quite likely to be satisfied, as we shall see in the following lemma and proposition.

@@

\section{Complications and improvements}
\label{section:remarks} \todo{Bas, het is niet alleen werk van anderen, hopelijk is het nu duidelijker}
In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous section to real cases.
\begin{itemize} 
\item Even if $r \geq g$, it might still be possible that $\overline{J(\Z)}$ coincidentally has dimension $r'$ smaller than $r$ (for example, if $r > g$); then one can find a rank $r'$ subgroup of $J(\Z)$ with the same closure inside $J(\Z_p)$, and do computations in this subgroup; we can expect this to work if $r' < g$. We can even use this to improve our calculations if we already have $r < g$, but $r'$ is even smaller. On the other hand, if $J(\Z)$ is dense in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
\item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$. It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \citep{Balakrishnan19}, where Coleman-Chabauty is used on a whole database of curves. They treat several possible cases and examples where the set is bigger. For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ is non-$p$-torsion, and then $Q-b$ also lies in the closure of $J(\Z)$.\todo{Nee, niet echt, hun argument is anders omdat ze Coleman-Chabauty doen}
\item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$. In general, finding generators of $J(\Z)$ is computationally out of reach, and one may need to assume the BSD conjecture to even find the rank $r$. However, note that one does not need to find all of $J(\Z)$; if we can generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$. For this, we only need to generate sufficiently many independent points of the Jacobian, and saturate subgroups with respect to some primes. Both of these feats are easier than finding all of $J(\Z)$.
\item Even this method does not work for a certain prime $p$, and neither for some other primes we tried, we can still use parts of the information we have learned. For example, maybe the method tells us that we have found all points of $J(\Z)$ stemming from $C(\Z)$ except those in a certain fibre of the map $J(\Z) \to J(\F_p)$. We can then aggregate this information for different primes, by looking at the maps $J(\Z) \to \prod_{p \in S} J(\F_p)$ for some set $S$ of primes of good reduction. See for example \citep{stoll10} for an introduction to the Mordell-Weil sieve.
\end{itemize}

@@

We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Both over $\Q_p$ and over $\F_p$ we have the equality
\[
\Lcal(2D_0 - D_{\text{aff}}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+))
\]
and then it should follow over $\Z_p$ so over $\Z/p^k\Z$. \todo{Bas, ik wilde je nog vragen over de [Todo]}[TODO:It is not necessarily true that a map that is an isomorphism when tensored with $\F_p$ and $\Q_p$ it is an isomorphism, but that is of course true if the map is between free modules, as I think it is here, right? As everything embeds into $\Z_p^n$ by evaluating at points, and submodule of free is free]

For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate the spaces $W_n := \Lcal(2D_0 - n\infty_-)$. For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots$, $x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \citep{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}\]. This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$. Finally, we have
\[
\Lcal((g+1)\infty_- + (g+1+d)\infty_+) = \{ s \in \Lcal((g+1+d)(\infty_+ + \infty_-)) \mid sx^{g+1-d} \in W_d).
\] 
Once again noting that we can write down an explicit basis for the space $\Lcal((g+1+d)(\infty_+ + \infty_-))$, this allows us to calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and to finish the computation.
\end{proof}

@@

\section{An explicit example}
\label{section:example}
We treat the hyperelliptic curve $C$ with first affine chart given by
\[
y^2 = f(x) = x^6+ 8x^5+ 22x^4+ 22x^3+ 5x^2+ 6x+ 1.
\]
This curve has genus $2$, and the Mordell-Weil group is isomorphic to $\Z$. This curve is also treated in Example~8.2 of \citep{poonen12}.

@@

Code for the calculations in this section can be found in \citep{spelier2020}.
\todo{Bas, hiervoor ben ik nu gegaan}

\section{Quadratic Chabauty}
\label{section:quadratic}
In this section we attempt to give an introduction to the article~\citep{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace. We will omit any proofs. For further reading, see for example \citep{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.

>>>>

\newcommand{\den}{\mathop{\mathgroup\symoperators den}\nolimits}
\newcommand{\ggd}{\mathop{\mathgroup\symoperators ggd}\nolimits}
\newcommand{\des}{\text{d.e.s.d.a.\ }}
%\newcommand{\opg}{\text{d.e.s.d.a.\ }}
\newcommand{\blokje}{\hfill $\Box$\\}
%Om je bewijs of je antwoord af te sluiten.
\newcommand{\header}[1]{\vspace{0.5cm}\framebox[\linewidth]{\textsc{Exercise #1}}\\}
\newcommand{\deel}[1]{\textbf{#1)}\ }
\newcommand{\macht}[1]{\mathcal{P}(#1)}
\newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\A}{\mathbb{A}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\G}{\mathbb{G}}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Fcal}{\mathcal{F}}
\newcommand{\Lcal}{\mathcal{L}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\NP}{\mathcal{NP}}
\newcommand{\NPC}{\mathcal{NPC}}
\newcommand{\F}{\mathbb{F}}
\renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand{\rad}{\text{rad}}
\newcommand{\x}{x}
\newcommand{\m}{\mathfrak{m}}
\newcommand{\tensor}{\otimes}
\newcommand{\Ring}{\textbf{Rings}}
\newcommand{\Sets}{\textbf{Sets}}

@@

This was later made into an effective argument by Coleman in 1985. This was done by finding explicitly, as a power series, a differential form $\omega$ on $J_{\Z_p}$ whose Coleman integral vanishes on $J(\Z)$. Pulling $\omega$ back to $C_{\Z_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Z)$ reducing to $P$ based only on finite-precision calculations of $\omega$. Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the introductory article \cite{poonen12}.

This Coleman-Chabauty method has been greatly generalised by Kim to so called non-abelian Chabauty. He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group. Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk in 2017 famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \cite{cursedcurve}. They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.

Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty'' \cite{edixhoven20}. Their goal in this article is to make a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian. They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve inside $T(\Z_p)$ along this map.

@@

Next, in Section~\ref{section:explicit} we focus on how to perform the calculations happening in the Jacobian. Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space. We partially follow the article \cite{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.

@@

\begin{rem}
\label{rem:smoothpointsfunc}
Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p)$, $y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\widetilde{Y}_y^p \to \widetilde{X}_x^p$. This is a direct consequence of II.7.15 of \cite{hartshorne}.
\end{rem}

@@

We will prove this using results about formal group as defined in \cite{honda70}. To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
First we introduce some notation that will be used in this section. Let $R$ be a commutative ring, and $x = (x_1,\dots,x_n)$ and sometimes $y,z$ are vectors of variables. Then $R[[x]]$ denotes as usual the ring of formal powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$. With $x = (x_1,\dots,x_n)$ and $y = (y_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$. Then for $g \in R[[y]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get \[g\circ f := (g_1(f(x)),\dots,g_k(f(x)))\in R[[x]]]^k.\] This definition makes sense because $f^i$ converges to $0$, so the infinite sum $g_j(f(x))$ converges.

@@

Now we will look at the theory of formal groups, and how that will help us. For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \cite{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \diff x_j$. If the formal group is furthermore commutative, then by Proposition~1.3 of \cite{honda70} these are closed, i.e. $d\omega_j = 0$. A $1$-form $d\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$. From now on, assume $R$ has no torsion; then $R$ imbeds into $\Q \tensor R$ and, we can formally integrate $\omega$, i.e. write it as $df$ where $f \in (\Q\tensor R)[[x]]$. We make this unique by demanding that $f(0) = 0$. Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[x]]$.

In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[x]]$ such that $d\log_i = \omega_i$. Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \cite{honda70}, this logarithm satisfies $\log(x) = x \bmod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$. By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]]$, and also satisfying $\exp(x) = x \bmod (x)^2$.
\addtocounter{thm}{-1}
\begin{exmp}[continued]
Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \cite{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$. The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$ (note this is a translate of the $\log$ from analysis), and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis). Then analysis will also explicitly tell us what $\exp$ looks like: namely, $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
\end{exmp}
\addtocounter{thm}{2}

@@

Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z)_P$. There are several, sometimes ad hoc, ways of proving finiteness. We start by looking simply at calculations modulo $p$. We let $I$ denote the ideal inside $\Z_p\angle{x_1,\dots,x_r}$ generated by $\lambda_1,\dots,\lambda_{g-1}$, and $A$ the quotient $\Z_p\angle{x_1,\dots,x_r}/I$. Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from \cite{edixhoven20}.

@@

Of note is that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \cite{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction. To summarise: in proposition~\ref{prop:linchabauty} we sacrifice certainty for being to able to prove much sharper bounds. However, a simple heuristic analysis shows that the conditions are quite likely to be satisfied, as we shall see in the following lemma and proposition.

@@

\section{Complications and improvements}
\label{section:remarks} \todo{Bas, het is niet alleen werk van anderen, hopelijk is het nu duidelijker}
In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous section to real cases.
\begin{itemize} 
\item Even if $r \geq g$, it might still be possible that $\overline{J(\Z)}$ coincidentally has dimension $r'$ smaller than $r$ (for example, if $r > g$); then one can find a rank $r'$ subgroup of $J(\Z)$ with the same closure inside $J(\Z_p)$, and do computations in this subgroup; we can expect this to work if $r' < g$. We can even use this to improve our calculations if we already have $r < g$, but $r'$ is even smaller. On the other hand, if $J(\Z)$ is dense in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
\item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$. It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \cite{Balakrishnan19}, where Coleman-Chabauty is used on a whole database of curves. They treat several possible cases and examples where the set is bigger. For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ lies in $J(\Z_p)_0$ and is non-$p$-torsion in $J(\Z_p)_0/J(\Z)_0$; then, as $J(\Z_p)$ is isomorphic as continous group to $\Z_p^g$, the point $Q-b$ lies in $\overline{J(\Z)_0}$, and clearly also in $C(\Z_p)$.\todo{Bas, explanation added}
\item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$. In general, finding generators of $J(\Z)$ is computationally out of reach, and one may need to assume the BSD conjecture to even find the rank $r$. However, note that one does not need to find all of $J(\Z)$; if we can generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$. For this, we only need to generate sufficiently many independent points of the Jacobian, and saturate subgroups with respect to some primes. Both of these feats are easier than finding all of $J(\Z)$.
\item Even this method does not work for a certain prime $p$, and neither for some other primes we tried, we can still use parts of the information we have learned. For example, maybe the method tells us that we have found all points of $J(\Z)$ stemming from $C(\Z)$ except those in a certain fibre of the map $J(\Z) \to J(\F_p)$. We can then aggregate this information for different primes, by looking at the maps $J(\Z) \to \prod_{p \in S} J(\F_p)$ for some set $S$ of primes of good reduction. See for example \cite{stoll10} for an introduction to the Mordell-Weil sieve.
\end{itemize}

@@

We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Over $\F_p$ we have the equality
\[
\Lcal(2D_0 - D_{\text{aff}}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+)).
\]
Note all these Riemann-Roch spaces are of the form $H^0(C_{\F_p},\Fcal_{\F_p})$ where $\Fcal$ is a sheaf on $C_{\Z_p}$ of degree higher than $2g-2$. Hence by Serre duality, $h^{1}(C_y,\Fcal_y)$ is $0$ for all $y \in \Spec \Z_p$. Then as the Euler characteristic is constant, also $h^{0}(C_y,\Fcal_y)$ is constant. By III.12.9 of \cite{hartshorne}, we see the basechange morphism $H^0(C_{\Z_p},\Fcal_{\Z_p}) \tensor \F_p \to H^0(C_{\F_p},\Fcal_{\F_p})$ is an isomorphism and $H^0(C_{\Z_p},\Fcal_{\Z_p})$ is a free $\Z_p$-module. That means this equality also holds over $\Z_p$, and hence over $\Z/p^k\Z$. then it should follow over $\Z_p$ so over $\Z/p^k\Z$. \todo{Bas, dit is het huidige argument}

For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate the spaces $W_n := \Lcal(2D_0 - n\infty_-)$. For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots$, $x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \cite{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}\]. This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$. Finally, we have
\[
\Lcal((g+1)\infty_- + (g+1+d)\infty_+) = \{ s \in \Lcal((g+1+d)(\infty_+ + \infty_-)) \mid sx^{g+1-d} \in W_d).
\] 
Once again noting that we can write down an explicit basis for the space $\Lcal((g+1+d)(\infty_+ + \infty_-))$, this allows us to calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and to finish the computation.
\end{proof}

@@

\section{An explicit example}
\label{section:example}
We treat the hyperelliptic curve $C$ with first affine chart given by
\[
y^2 = f(x) = x^6+ 8x^5+ 22x^4+ 22x^3+ 5x^2+ 6x+ 1.
\]
This curve has genus $2$, and the Mordell-Weil group is isomorphic to $\Z$. This curve is also treated in Example~8.2 of \cite{poonen12}.

@@

Code for the calculations in this section can be found in \cite{spelier2020}.
\todo{Bas, hiervoor ben ik nu gegaan}

\section{Quadratic Chabauty}
\label{section:quadratic}
In this section we attempt to give an introduction to the article~\cite{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace. We will omit any proofs. For further reading, see for example \cite{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
